---
title: "metrnalysis"
description: |
  How are Meta-analysis packages inter-related?
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)
library(cranlogs)
library(RCurl)
library(XML)
library(stringr)
library(miniCRAN)
library(igraph)
library(visNetwork)

```

## Introduction

Which packages are available already for Meta-analysis in R and how are they inter-related? Using R functions to develop a dependency network we show that there are currently 95 R packages on CRAN that are focused on meta-analysis and 546 "supporting" packages that underpin functions in the meta-analysis packages. We then use thematic analysis to identify clusters of meta-analysis packages that (based on their description) carry out similar functions.  


## Visualisation of relationship between R packages that are used in Meta-analysis

To get a list of packages that are used in Meta-analysis we can have a look at the **CRAN task view for MetaAnalysis** ["https://CRAN.R-project.org/view=MetaAnalysis"]. Here is the top ten packages in the list (in no particular order).

```{r}
url<-"https://CRAN.R-project.org/view=MetaAnalysis" # location of CRAN task view

# Read in the names of the packages
html <- paste(readLines(url), collapse="\n")
matched <- str_match_all(html, "<a href=\"(.*?)\"")
matched2<-unlist(matched)
tst<-sub(".*/packages/","",matched2)
packages.list<-gsub("^(.*?)/.*", "\\1", tst)
packages.list<-packages.list[2:562]

pkgs<-data.frame("packages"= unlist(packages.list))
head(pkgs,10)
```


## Build a dependency graph

We can build a graph of the package dependencies to see how they are related to each other.

```{r}
tags <- c(packages.list)
dg <- makeDepGraph(tags, enhances = TRUE)
#sort(degree(dg))
Isolated = which(degree(dg)<10)
dg2 = delete.vertices(dg, Isolated)
#V(dg2)
vn <- toVisNetworkData(dg2)
vn$nodes$title<-vn$nodes$label
vn$nodes$group<-ifelse(vn$nodes$id %in% pkgs$packages==TRUE, "MetaAnalysis", "Supporting")
# Nodes are sized by degree (the number of links to other packages)
degree_value <- degree(dg2, mode = "all")
vn$nodes$value <- degree_value[match(vn$nodes$id, names(degree_value))]

visNetwork(nodes = vn$nodes, edges = vn$edges,main="Both",height = "500px", width = "100%")%>%
  visOptions(highlightNearest = TRUE)%>%
  visNodes(color="blue")%>%
  visSave(file =paste0(here(),"/Plots/both.html"), selfcontained = T)

```



